### 2023-03-14 chapter1/chapter1.tex
Added citation to transcriptomics of original 12 Drosophila genomes

To develop these methods, we chose a set of 33 assembled and annotated \textit{Drosophila} genomes, which includes all 12 species from the original \textit{Drosophila} 12 Genomes Consortium~\cite{D12GC2007}. However, the genomes of these 12 species have been re-sequenced since their first release, which has resulted in substantial improvements in their assemblies and annotations. Despite these developments and other several other recent genome assembly projects of species in the \textit{Drosophila} genus, there is not yet a collection of high-quality alignments of orthologous proteins that reflects these improvements in genome assembly and diversity~\cite{Miller2018, Kim2021}. Given the \textit{Drosophila} genus spans diverse habitats and over 50 million years of evolution but maintains a conserved life cycle and body plan, such a resource would facilitate a new generation of studies that illuminate the forces that drive protein evolution in unprecedented detail~\cite{Wiegmann2011, Obbard2012}.

>>>>

To develop these methods, we chose a set of 33 assembled and annotated \textit{Drosophila} genomes, which includes all 12 species from the original \textit{Drosophila} 12 Genomes Consortium~\cite{D12GC2007}. However, the genomes of these 12 species have been re-sequenced since their first release, which has resulted in substantial improvements in their assemblies and annotations~\cite{Yang2018, Miller2018}. Despite these developments and other several other recent genome assembly projects of species in the \textit{Drosophila} genus, there is not yet a collection of high-quality alignments of orthologous proteins that reflects these improvements in genome assembly and diversity~\cite{Kim2021}. Given the \textit{Drosophila} genus spans diverse habitats and over 50 million years of evolution but maintains a conserved life cycle and body plan, such a resource would facilitate a new generation of studies that illuminate the forces that drive protein evolution in unprecedented detail~\cite{Wiegmann2011, Obbard2012}.
